### 2020-05-05 thesis_template/0_Prelim/abs.tex
revise untill intro

Existing big data processing tools are developed on A

>>>>

% Motivation 
% - Faster computation and  saving computer resource is important 
% - introduce Big Data tool can be improve
% Problem description
% - introduce Spark, MapReduce is implemented in Application Language.
% - some problems
% Concept 
% - use of rust 
% - what is core concept of experiment
% Evaluation
% - how to evaluate that
% - some notable result

Planning optimized memory management is critical for Big Data analysis tools to perform faster runtime and efficient use of computation resources.
Modern Big Data analysis tools are developed with application languages that abstract their memory management, so that developers do not have to pay extreme attention to memory management strategies.

Many existing Big Data processing tools are developed on Java Virtual Machine (JVM). 
Memory strategies in JVM, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
Apache Spark and Apache Flink use complex objects to manipulate and transfer tremendous amount of data. 
Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation.

Considered the problems in memory management in JVM, developing Big Data processing tools with system languages can be the solution.
By using a system language, a developer has control on memory management, so that one can implement systems with better optimized memory management strategies.
We selects Rust as good candidate for development of Big Data processing tools, due to its ability to write memory-safe and fearless concurrent codes with its concept of ownership.

There may be many possible strategies to optimize memory management for Big Data processing in Rust programming: 
selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.
We conduct several experiments to assess how much these different memory management strategies differ runtime performance of algorithms.

Our experiments focus complex object manipulation and common algorithms for Big Data processing with various memory management.
The results show significant difference among the algorithms using these different memory strategies.

### 2020-05-05 thesis_template/1_Intro/intro.tex
revise untill intro

\section{Motivation}
\label{sec:motivation}
Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies has democratized data driven businesses by 
eliminating significant amount of initial investment.

However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime. The memory-safety, and fearless concurrently in Rust programming 
make the language one of the ideal candidate for development of Big Data tools. 
Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
In this dissertation, we focus on memory management strategy for Big Data processing algorithms in development with Rust.

@@

Many of popular open source cluster computing frameworks for large scale data analysis, 
such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
which require iterative process. As the amount of data increases, memory is required to keep many objects. 
Therefore, memory management plays a critical role in this task.

One of the memory management tool on JVM is garbage collection. 
The garbage collection brings a significant advantage for programmers by removing responsibility
for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.

In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.

Considering the issue of memory management, we introduces solution based on unique memory management methods implemented in Rust, ownership , move and borrowing.
This unique concepts in Rust secure codes and perform memory management without monitoring memory. 
Since developer can select variety of memory management strategies to implement Big Data processing algorithms in Rust.
We develop such algorithms with different strategies and compare their runtime performance to study the best algorithm implementation.

>>>>

\section{Motivation}
\label{sec:motivation}
Cluster computing tool for Big Data Analysis has been more important as magnitude and quality of data that we can obtain increases. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies has democratized data driven businesses by 
eliminating significant amount of initial investment.

However these computation resources do not come for free; we need to pay money to use these resources. Usually, user needs to pay depending on usage of computational resources. 
If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

Rust is a system language which gives the similar performance and control of hardware to C++ or C and safety of runtime. The memory-safety, and fearless concurrently in Rust programming 
make the language one of the ideal candidate for development of Big Data tools. 
Since the design of the language is different from any other programming languages, implementations that can be selected for algorithms can differ from existing ones.
In this thesis, we focus on memory management strategy for Big Data processing algorithms in development with Rust.

@@

% Many of popular open source cluster computing frameworks for large scale data analysis, 
% such as Hadoop and Spark, allow programmers to define objects in a host languages, such as Java.
% The objects are then managed in RAM by the language and its runtime, Java Virtual Machine 
% in the case of Java and Scala. Storing objects in memory enables machine to process iterative computation. 
% One of the fundamental tasks for recent big data analysis is analysis using Machine Learning Algorithms, 
% which require iterative process. As the amount of data increases, memory is required to keep many objects. 
% Therefore, memory management plays a critical role in this task.

% One of the memory management tool on JVM is garbage collection. 
% The garbage collection brings a significant advantage for programmers by removing responsibility
% for planning memory management by themselves manually. Instead, JVM monitors the state of memory and performs garbage
% collection at certain points. However, these monitoring and auto-execution of garbage collection cost additional 
% computation and might consume computation resources which should be used for data processing. This can significantly decrease performance of the computation.

% In contrast, memory management in system language, such as C++, relies on programmers’ decision for when to allocate and deallocate memory. 
% The functions, malloc/free consume most of the memory management. Proper implementation of system language for big data processing can be overperform the implementation in host language.
% Nevertheless, implementing C++ performing proper memory management and guaranteeing security can be unproductive and complicated.

Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.

Rust has various ways to manage memory. Rust has different variable types for values allocated in sequence of memory region. 
Each variables take different memory representation that can produce variation of operation time on the variable types.

In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
Reference Counting has both advantage and disadvantage. 
Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.

Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.

As we can see, we can choose various memory management strategies in Rust programming.
Therefore, we assess following research question in this thesis.
\begin{itemize}
    \item What are better memory management strategies for complex object processing to perform faster runtime performance.
    \item How much impact do different variable types in Rust have in order to algorithms' runtime performance?
    \item How much can algorithms runtime be improved or degraded, if we use Reference Count?
    \item What are better memory management strategies for faster Big Data processing in Rust multithreading?
    \item How can we improve runtime performance of common Big Data algorithms by Rust memory management?
\end{itemize}

To answer these question, we conduct 5 experiments.

### 2020-05-05 thesis_template/2_RelatedWork/model/intro.tex
revise untill intro

This chapter describes background knowledge that we have studied for our research.
In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
Knowledge of operating systems helps us to understand how operating systems handle memory management and 
how other technologies takes advantage of them. Even though this dissertation does not focus technologies used for Linear Algebra Computation, 
there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
It worths to study these concepts explained in Section~\ref{sec:linalg}. 
In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 
Then, Section~\ref{sec:spark} details technologies used for Apache Spark, which is one of the most popular tools for Big Data processing.
In Section~\ref{sec:appsys} and Section~\ref{sec:rustmem}, the advantages of using System Language and Rust for such tools are discussed respectively.
Finally, Section~\ref{sec:llvm} describes how LLVM thrives computer language development.

>>>>

This chapter describes the related work and concepts to our research in this thesis. 
In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
Knowledge of operating systems helps us to understand how operating systems handle memory management and 
how other technologies takes advantage of them. Even though this thesis does not focus technologies used for Linear Algebra Computation, 
there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
It worths to study these concepts explained in Section~\ref{sec:linalg}. 
In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 
Then, Section~\ref{sec:spark} details technologies used for Apache Spark, which is one of the most popular tools for Big Data processing.
In Section~\ref{sec:appsys} and Section~\ref{sec:rustmem}, the advantages of using System Language and Rust for such tools are discussed respectively.
Finally, Section~\ref{sec:llvm} describes how LLVM thrives computer language development.
